Capstone Movielens Report

### 2025-12-08 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
UMGYDE Model description started (prototype added to Appendix A).

This is a helper function that calculates the _Day General Effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.

@@

This is a helper function that calculates the _Day General Effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset using the _5-Fold Cross Validation_ and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv)) described below.

@@

This is a helper function that calculates the _Smoothed Day Effect_ of user ratings and is intended to be used in other functions and scripts (such as [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect)) described below.

@@

This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.

@@

This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv)) described below.

>>>>

This is a helper function that calculates the _Day General Effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset and is intended to be used in other custom functions (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.

@@

This is a helper function that calculates the _Day General Effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset using the _5-Fold Cross Validation_ and is intended to be used in other custom functions (such as [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv)) described below.

@@

This is a helper function that calculates the _Smoothed Day Effect_ of user ratings and is intended to be used in other custom functions (such as [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect)) described below.

@@

This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other custom functions (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.

@@

This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other custom functions (such as [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv)) described below.
